Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-13 analysis/paper/paper.qmd
Supplemental figures

@@

During the 5 survey years, we sighted a total of 22 species of seabirds and marine mammals ([@tbl-predators]). The most abundant species were snow petrels, Adélie penguins, and Antarctic fur seals. The most widespread species observed were snow petrels, Antarctic petrels, and southern giant petrels. The 6 most abundant species (total individuals observed in @tbl-predators) averaged across years were widely distributed across the study region, although densities varied by species ([@fig-top6map]). Distribution maps of all seabird (Fig. S1) and marine mammal species (Fig. S2) are provided in the Supplement. We observed predators in proximity (15 km, 3 d) to 245 sampling stations, ranging from 19 stations in 2012 to 68 stations in 2014. Each station was associated with 30.2 ± 10.3 km (mean ± SD) of visual survey effort ([@supptbl-effortice]).

@@

| Variable                   | Description and units                                                                                                                                                                                                                                                                                                 | Collection location |
|:----------------|:--------------------------------------|:----------------|
| UML depth                  | Depth at which the density differed by 0.05 kg m^−3^ from the average density of the upper 10 m of the water column [@mitchell1991] \[meters\]                                                                                                                                                                        | Station             |
| Temperature                | Average UML temperature \[°C\]                                                                                                                                                                                                                                                                                        | Station             |
| Salinity                   | Average UML salinity \[PSU\]                                                                                                                                                                                                                                                                                          | Station             |
| Chl *a*                    | Average integrated chl *a* to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                         | Station             |
| Phaeopigment               | Average integrated phaeopigment to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                    | Station             |
| Ice type                   | Factor with 4 levels: open, thin, first-year, multi-year                                                                                                                                                                                                                                                              | Transect            |
| Ice coverage               | Percent cover                                                                                                                                                                                                                                                                                                         | Transect            |
| Macrozooplankton community | Factor with 5 levels corresponding to the clusters identified by @dietrich2021winter: 1 (*Salpa* and *Clione*), 2a (small *Euphausia*, myctophid larvae, and amphipods), 2b (*Thysanoessa*), 3a (extremely diverse, including siphonophores, chaetognaths, copepods), and 3b (*E. superba* and *E. crystallorophias*) | Station             |

@@

>>>>

      key: suppfig
      reference-prefix: Fig. S
      caption-prefix: Figure S
      latex-env: suppfig

@@

During the 5 survey years, we sighted a total of 22 species of seabirds and marine mammals ([@tbl-predators]). The most abundant species were snow petrels, Adélie penguins, and Antarctic fur seals. The most widespread species observed were snow petrels, Antarctic petrels, and southern giant petrels. The 6 most abundant species (total individuals observed in @tbl-predators) averaged across years were widely distributed across the study region, although densities varied by species ([@fig-top6map]). Distribution maps of all seabird ([@suppfig-birdclim]) and marine mammal species ([@suppfig-mammclim]) are provided in the Supplement. We observed predators in proximity (15 km, 3 d) to 245 sampling stations, ranging from 19 stations in 2012 to 68 stations in 2014. Each station was associated with 30.2 ± 10.3 km (mean ± SD) of visual survey effort ([@supptbl-effortice]).

@@

| Variable                   | Description and units                                                                                                                                                                                                                                                                                                 | Collection location |
|:-----------------|:------------------------------------|:-----------------|
| UML depth                  | Depth at which the density differed by 0.05 kg m^−3^ from the average density of the upper 10 m of the water column [@mitchell1991] \[meters\]                                                                                                                                                                        | Station             |
| Temperature                | Average UML temperature \[°C\]                                                                                                                                                                                                                                                                                        | Station             |
| Salinity                   | Average UML salinity \[PSU\]                                                                                                                                                                                                                                                                                          | Station             |
| Chl *a*                    | Average integrated chl *a* to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                         | Station             |
| Phaeopigment               | Average integrated phaeopigment to 100 m from bottles \[mg m^-2^\]                                                                                                                                                                                                                                                    | Station             |
| Ice type                   | Factor with 4 levels: open, thin, first-year, multi-year                                                                                                                                                                                                                                                              | Transect            |
| Ice coverage               | Percent cover                                                                                                                                                                                                                                                                                                         | Transect            |
| Macrozooplankton community | Factor with 5 levels corresponding to the clusters identified by @dietrich2021winter: 1 (*Salpa* and *Clione*), 2a (small *Euphausia*, myctophid larvae, and amphipods), 2b (*Thysanoessa*), 3a (extremely diverse, including siphonophores, chaetognaths, copepods), and 3b (*E. superba* and *E. crystallorophias*) | Station             |

@@

## Supplemental figures

::: {#suppfig-birdclim}
```{r}
#| label: suppfig-birdclim
#| fig-height: 7.15
#| fig-width: 6.5
make_fig_predclim(read_obj("pred_class_df"),
                  c("Blue petrel",
                    "Antarctic shag",
                    "Cape petrel",
                    "Kelp gull",
                    "Antarctic petrel",
                    "Southern giant\npetrel",
                    "Adélie penguin",
                    "Kerguelen petrel",
                    "Gentoo penguin",
                    "Antarctic tern",
                    "Northern giant\npetrel",
                    "Pale-faced\nsheathbill",
                    "Chinstrap penguin",
                    "Southern fulmar",
                    "Antarctic prion",
                    "Common diving\npetrel",
                    "South polar skua",
                    "Snow petrel",
                    "Emperor penguin",
                    "Black-browed\nalbatross"),
                  nrow = 4)

Geographic distributions of seabird species observed during visual surveys, averaged across years.
:::

::: {#suppfig-mammclim}
```{r}
#| label: suppfig-mammclim
#| fig-height: 7.6
#| fig-width: 6.5
make_fig_predclim(read_obj("pred_class_df"),
                  c("Antarctic fur seal",
                    "Leopard seal",
                    "Bottlenose whale",
                    "Crabeater seal",
                    "Elephant seal",
                    "Killer whale",
                    "Weddell seal",
                    "Ross seal",
                    "Minke whale"),
                  nrow = 3)

Geographic distributions of marine mammal species observed during visual surveys, averaged across years.
:::
